Reproducible Research Project
_____________________________

```{r}
library(stats)
library(dplyr)
library(ggplot2)
```

##Loading and preprocessing the data.
### Download and read data.frame.

```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl,destfile="./data/activity.zip")
filename <- unzip("activity.zip")
if(!file.exists("./ActivityData")){dir.create("./activityData")}
ActivityData <- read.csv("activity.csv", header = T, sep = ",", na.strings = "NA")
ActivityData$date<-as.Date(ActivityData$date, "%Y-%m-%d")
ActivityData$steps <- as.numeric(ActivityData$steps)
ActivityData$interval <- as.numeric(ActivityData$interval)
head(ActivityData)
str(ActivityData)
dim(ActivityData)  
summary(ActivityData)  
```

### Change format

```{r}
ActivityData$date <- as.Date(ActivityData$date)
summary(is.na(ActivityData$steps))
ActivityData$DateTime<- as.POSIXct(ActivityData$date, format="%Y-%m-%d")
```

##1- What is mean total number of steps taken per day?
### We need see missing values

#### Remove missing values, so we created a functinon call Total_activity.

```{r}
Total_activity <- ActivityData[which(!is.na(ActivityData$steps)),]
Activitydays <- tapply(Total_activity$steps, Total_activity$date, sum)
```

### It,s time to aggregate the data by day and create a histogram.

```{r}
hist(Activitydays, main = "Total steps taken each day",col = "light blue", xlab = "Steps", ylab = "Date")
head(Activitydays)
```

### To calculate mean and median of the total number os steps taken day.

```{r}
Mean_Steps <- mean(Activitydays, na.rm = TRUE)
Mean_Steps

Median_Steps <- median(Activitydays, na.rm=TRUE)
Median_Steps
```

##2 What is the average daily activity pattern?
###2.1 Time series plot of the 5-minute interval and the average number of steps taken, averaged across all days.

####Cleaning Nas

```{r}
ActivityDataNonNAs <- ActivityData[!is.na(ActivityData$steps),]
ActivityDataNonNAs
```

####Average number of steps per interval.

```{r}
AVGstepsByInterval <-  ActivityData%>%
  group_by(interval)%>%
  filter(!is.na(steps))%>%
  summarise(avg_steps = mean(steps, na.rm=TRUE))
AVGstepsByInterval
```
 
##2.2 Creating the historgram of total steps per day

```{r}
ggplot(AVGstepsByInterval, aes(x =interval , y=avg_steps)) +
  geom_line(color="red", size=1) +
  labs(title = "Average Daily Steps", x = "Interval", y = "Average Steps Per Day")
```

##3. Are there differences in activity patterns between weekdays and weekends?
###3.1 Create a factor with 2 levels: Weekend and Weekday. 

```{r}
ActivityDataNonNAs$Weekdays <- weekdays(ActivityDataNonNAs$date) 
ActivityDataNonNAs$Weekend <- ifelse (ActivityDataNonNAs$Weekdays == "Saturday" | ActivityDataNonNAs$Weekdays == "Sunday", "Weekend", "Weekdays")
head(ActivityDataNonNAs,5)
```

###3.2 Make a serial plot containing a time series plot

```{r}
WeekendTable <- aggregate(ActivityDataNonNAs$steps, by=list(ActivityDataNonNAs$Weekend, ActivityDataNonNAs$interval), mean)
names(WeekendTable)[1] ="Weekend"
names(WeekendTable)[2] ="interval"
names(WeekendTable)[3] ="steps"

plot <- ggplot(WeekendTable, aes(x = interval, y = steps, color= Weekend)) +
  geom_line() +
  facet_grid(Weekend ~ .) +
  labs(title = "MEAN OF STEPS", x = "interval", y = "steps")
print(plot)
```
